Home Nighttime Cough Monitoring

### 2025-01-24 Lilah Melzer/cough_monitor_analysis.qmd
started CFQ-R surveys

```{r setup}
#| include: false
library(Hmisc)
library(redcapAPI)
library(tidyverse)
library(rspiro)
library(childsds)
library(arsenal)
library(lmerTest)
library(performance)
library(GLMMadaptive)
library(gt)
```

@@

# I

@@

```{r results='asis'}
#| label: fig-coughs-by-night-2
#| fig-cap: Coughs by nights from start
#| warning: false
invisible(lapply(unique(agg_counts$sid), function(s) {
  if (s == 3) {
    d <- agg_counts[agg_counts$sid == s & agg_counts$Night %in% c(1:7, 96:102), ]
  } else {
    d <- agg_counts[agg_counts$sid == s & !is.na(agg_counts$Coughs), ]
  }

  diag <- d$Diagnosis[1]
  p <- ggplot(d, aes(
    x = Night, y = Coughs, group = factor(sid), color = Sick
  )) +
    geom_point() +
    geom_line() +
    theme_bw() +
    ylim(0, 50) +
    xlim(0, 147) +
    scale_color_manual(values = c("#377EB8", "#E41A1C")) +
    ggtitle(paste0("Participant ", s, " (", diag, ")"))
  if (s == 38) {
    p <- p + ylim(0, 270)
  }
  cat("\n")
  cat("\n")
  print(p)
  cat("\n")
  cat("\n")
}))
```

>>>>

```{r setup}
#| include: false
library(Hmisc)
library(redcapAPI)
library(rspiro)
library(childsds)
library(arsenal)
library(lmerTest)
library(performance)
library(GLMMadaptive)
library(tidyverse)
library(ggstats)
```

@@

@@

```{r results='asis'}
#| label: fig-coughs-by-night-2
#| fig-cap: Coughs by nights from start
#| warning: false
invisible(lapply(unique(agg_counts$sid), function(s) {
  d <- agg_counts[agg_counts$sid == s, ]
  diag <- d$Diagnosis[1]
  p <- ggplot(d, aes(
    x = Night, y = Coughs, group = factor(sid), color = Sick
  )) +
    geom_point() +
    geom_line() +
    theme_bw() +
    ylim(0, 50) +
    xlim(0, 150) +
    scale_color_manual(values = c("#377EB8", "#E41A1C")) +
    ggtitle(paste0("Participant ", s, " (", diag, ")"))
  if (s == 38) {
    p <- p + ylim(0, 270)
  }
  cat("\n")
  cat("\n")
  print(p)
  cat("\n")
  cat("\n")
}))
```

# CFQ-R

```{r}
# CFQ-R Caregivers 6-13
cfqr_6_13 <- df %>%
  filter(redcap_repeat_instrument == "CFQ-R Caregivers 6-13") %>%
  select(sid, Diagnosis, cfqr_caregivers_613_timestamp:cfqr_caregivers_613_complete)
```
